---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing
```{r}
data <- read.csv("C://Users//Marcio Vianna Filho//Dropbox//Coursera//Reproducible research//Assignment 1//RepData_PeerAssessment1//activity//activity.csv")
```


## What is mean total number of steps taken per day?
1. Histogram of steps taken each day
```{r}
agrData <- aggregate(data$steps, by=list(data$date), FUN=sum)
hist(agrData[,2], 
     main="Number of Steps per Day",
     xlab="steps")
```

2. Mean and median total number of steps taken per day
```{r}
avSteps <- mean(agrData[,2], na.rm=T)
medSteps <- median(agrData[,2], na.rm=T)
print(paste("The number of steps taken per day has an average of", avSteps, "and a median of", medSteps, "in the observed period."))
```


## What is the average daily activity pattern?
1. Make a time series plot (i.e. type = "l" ) of the 5-minute interval (x-axis)
and the average number of steps taken, averaged across all days (y-axis)
```{r}
agrData <- aggregate(data$steps, by=list(data$interval), FUN=mean, na.rm=T)
plot(agrData[,1], agrData[,2], type="l",
     main="Average Number of Steps per Time Intervals\nAccross All Considered Days",
     xlab="time interval",
     ylab="steps")
```

2. Which 5-minute interval, on average across all the days in the dataset,
contains the maximum number of steps?
```{r}
maxSteps <- max(agrData[,2])
interMaxsteps <- agrData[agrData[,2]==maxSteps,][,1]
print(paste("The interval with the maximum number of steps is interval", interMaxsteps, "with", maxSteps, "steps taken on average."))
```
## Imputing missing values
1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NA s)
```{r}
needsRepl <- is.na(data[,1])
nrow(data[needsRepl,])
```

2. Devise a strategy for ???lling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.
```{r}
newSteps <- merge(data, agrData, by.x=3, by.y=1)
new <- ifelse(is.na(newSteps$steps), newSteps$x, data[,1])
```



3. Create a new dataset that is equal to the original dataset but with the
missing data ???lled in.
4. Make a histogram of the total number of steps taken each day and Calculate
and report the mean and median total number of steps taken per day. Do
these values di???er from the estimates from the ???rst part of the assignment?
What is the impact of imputing missing data on the estimates of the total
daily number of steps?


## Are there differences in activity patterns between weekdays and weekends?
